THESIS PROJECT PROPOSAL

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are massless, they 
do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are not possible at 
tree level and can only proceed via loop diagrams which involve vector bosons or heavy quarks(t,b,c) in the loop.

>>>>

The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are massless, they 
do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are not possible at 
tree level and can only proceed via loop diagrams which involve W boson or top quark in the loop.
